---
title: "Immigration Project"
author: "Saiyaz Kazi"
date: "10/18/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)
library(dplyr)

z <- read_csv("anes_timeseries_cdf.csv")
```

```{r echo=FALSE}
x <- z %>% 
   nrow()

```

My project focuses on trying to track the political voting patterns of immigrants throughout the last decades. The data I am using is from the American National Election Studies' time-series collective data from 1948-2016. Using this data and the ANES codebook, I sohuld be able to isolate for immigrants, location, and then aggregate voting tendencies per state. Hopefully my end product will be a leaflet based program that shows you per decade per state the ratio between democratic/republic votes of immigrants. Tracking that over the years could be useful in seeing, if there, voting patterns, shifts, or critical turns in the aggregate immigrant electoral patterns.

Number of ANES Observations: `r x`

